---
title: "Create Codelist"
subtitle: "Rheumatorlogy"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    code_folding: hide
    toc: true
    toc_depth: 3
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

# Load pkgs and funs

```{r, class.source = 'fold-show'}
# R packages
library(reactable)
library(tidyverse)
library(here)
library(dbplyr)
library(readr)
library(bigrquery)
library(DBI)

# Helper fun connecting to bigquery
source(here("scripts/connect_bigquery.R"))

# Helper function to write SQL queries
source(here("scripts/create_ingredient_lookup_sql.R"))

```

# Define ingredients

```{r, class.source = 'fold-show'}
# Define product list for lookup
ingredient_list <- c('Adalimumab', 'Etanercept', 'Certolizumab', 
                     'Infliximab', 'Golimumab','Rituximab',
                     'Tocilizumab','Sarilumab','Tofacitinib',
                     'Baricitinib','Upadacitinib','Filgotinib',
                     'Abatacept','Ipilimumab','Nivolumab',
                     'Pembrolizumab')
```

# Create SQL queries

```{r, class.source = 'fold-show'}
# With wildcards
sql_wild_ingredients <- create_ingredient_lookup_sql(ingredient_list, 
                                                     wildcards = TRUE,
                                                     return = "sql")

```

The code of the function `create_ingredients_lookup_sql()` is available in the chunk below:

```{r code = readLines(here('scripts/create_ingredient_lookup_sql.R'))}

```

# Show SQL query

## Wildcards

```{r, class.source = 'fold-show'}
cat(sql_wild_ingredients)
```

# Show results

- Using SQL codes with wildcards 

```{r, cache=TRUE}
df_ingredients <- dplyr::tbl(conn_ebm_dmd, sql_wild_ingredients) %>% 
  collect() %>% 
  arrange(id)
```

## ddd availability

The table below shows the number of products (`n`) with available daily defined dose (`ddd_available`) information in our database.
More information can be found in the table with detailed information at the end of this document.

```{r}

df_ingredients %>% 
  group_by(ingredient) %>% 
  count("ddd_available" = !is.na(ddd), name = "n") %>% 
  reactable(filterable = TRUE,
            style = list(fontSize = "12px"),
            highlight = TRUE)

```

## Detailed information

```{r}

df_ingredients %>% 
  reactable(filterable = TRUE,
            groupBy = "ingredient",
            columns = list(
              type = reactable::colDef(minWidth = 30),
              id = reactable::colDef(minWidth = 60),
              bnf_code = reactable::colDef(minWidth = 100),
              nm = reactable::colDef(minWidth = 200),
              ingredient = reactable::colDef(minWidth = 100),
              ddd = reactable::colDef(minWidth = 30)
            ),
            style = list(fontSize = "12px"),
            highlight = TRUE
)
```

# Write .csv

- The .csv file is available [here](https://github.com/ebmdatalab/scmd-rheumatology/blob/main/data/rheumatology_meds.csv)

```{r}
# Uncomment this line and add correct file name 
write_csv(df_ingredients, file = here("data/rheumatology_meds.csv"))
```

